A performance comparison of Dask and Apache Spark for data-intensive neuroimaging pipelines

### 2019-10-01 latex/paper.tex
Modified GIL paragraph
        Expanded on our suggested configuration to avoid undesirable performance
    behaviour as in the Histogram (Python) application

This behavior is also the consequence of our configuration of Dask that
created 1 worker process with 8 threads. Since the Histogram Python
implementation does not release the GIL it can only use one of the thread
at a given time thus it slows down the computation significantly. This
behavior highlights the need to configure the workers properly depending on
the type of functions executed in an application.

>>>>

This behavior is also the consequence of our configuration of Dask that
created 1 worker process with 8 threads. Since the Histogram Python
implementation does not release the GIL it can only use one of the thread
at a given time thus it slows down the computation significantly. 
% This behavior highlights the need to configure the workers properly depending on
% the type of functions executed in an application. 
Our results suggest configuring Dask with multi-threaded workers for application
releasing the GIL and multi-process workers while the default configuration of Spark
workers brings stable results across different types of applications.
